---
title: "Challenge_Stats"
author: "Bernat"
date: "30 May 2019"
output: html_document
---
```{r}
getwd()
#setwd('C:/Users/Bernat/Desktop/template/bernat/Module_2_Statistics/5_Regression_Analysis')
#getwd()
```
#Import the data file

```{r}
data_set <- read.csv('GATT_TR_KR.csv')

data_set
```
#Import library and convert figures to non power format
```{r}
library(dplyr)
options("scipen" = 10)
options()$scipen
```
#Select specific columns. With this selection we gather country gdp, gdp per capita, trade and GATT belonging yes or not.
```{r}
gdpgroup_gatt_yes = select(data_set, year, rep_code, gdpp_rep, gdp_rep,gatt_dejure_rep,trade)
#gdpgroup

gdpgroup_gatt_yes=na.omit(gdpgroup_gatt_yes)
gdpgroup_gatt_yes
```
#In this selection we group the data by country and get the mean throught the 1973-1973 period....of the countries's GDP, and per capita GDP
```{r}
gdp_means<-aggregate(gdpgroup_gatt_yes[,3:5], list(gdpgroup_gatt_yes$rep_code), mean)
gdp_means
```
#In this selection we group the all info per year....we see the MEAN of whole world's economy as a total.
```{r}
year_means<-aggregate(gdpgroup_gatt_yes[,3:4], list(gdpgroup_gatt_yes$year),mean)
year_means
#type(year_means)
```
#In this selection we have the total trade on year basis.FOR THE COUNTRIES IN THE GATT
```{r}
trade<-aggregate((gdpgroup_gatt_yes$trade),list(gdpgroup_gatt_yes$year),sum)
#trade
names(trade)[1]='Year'
trade
```



```{r}
mean(trade$x)
means = replicate(10000, mean(sample(trade$x, size = 4, replace = TRUE)))
quantile(means, c(0.025, 0.975))
hist(means)
mean(means)
```
#Analysis GATT vs No GATT
```{r}
gdpgroup_gatt_yes = select(data_set, year,gatt_dejure_rep, rep_code, gdpp_rep, gdp_rep,trade)
#gdpgroup

gdpgroup_gatt_yes=na.omit(gdpgroup_gatt_yes)
gdpgroup_gatt_yes
```


```{r}
gatt_yes<-aggregate(gdpgroup_gatt_yes[,4:6], by = (gdpgroup_gatt_yes[1:2]), mean)
gatt_yes=gatt_yes[order(gatt_yes$year),]
gatt_yes
```


#3Q regression model. We chose Jamaica as reference country, and we will try to analyse their trading partners and mostly traded comms.
```{r}
data_set=na.omit(data_set)
Jamaica = filter(data_set,rep_code == 388)
#Jamaica
row.names(Jamaica)<-1:nrow(Jamaica)#index the DF
Jamaica
```
#In this selection, we filter out the rows where trade is 0.So we have the rows with trade by commodity code and partner.
```{r}
Jamaica = filter(data_set, year, rep_code == 388, gdpp_rep, gdp_rep,gatt_dejure_rep,trade >0)
nrow(Jamaica)
Jamaica
#reg<-lm(trade~distance+gdp_part+gdpp_part+gatt_defacto,data = Jamaica)
summary(reg)
```
#here we scale the numerical values by columns
```{r}
Jamaica$trade<-scale(Jamaica$trade)
Jamaica$gdpp_rep<-scale(Jamaica$gdpp_rep)
Jamaica$gdp_rep<-scale(Jamaica$gdp_rep)
Jamaica$pop_rep<-scale(Jamaica$pop_rep)
Jamaica$gdp_part<-scale(Jamaica$gdp_part)
Jamaica$pop_part<-scale(Jamaica$pop_part)
Jamaica$distance<-scale(Jamaica$distance)
Jamaica$gdpp_part<-scale(Jamaica$gdpp_part)
Jamaica

```

```{r}
reg<-lm(trade~distance+gdp_part+gatt_defacto_part+pop_part+island_part, data = Jamaica)
summary(reg)
```

#We select for Jamaica the specific columns of interest

```{r}
jam = select(Jamaica, year,comm_code, part_code,trade,gatt_dejure_rep)
jam

```
```{r}
library(varhandle)
dummies<-to.dummy(Jamaica$comm_code, "commodity" )

row.names(dummies)<-1:nrow(dummies)
dummies
```

```{r}
library(plyr)
nrow(Jamaica)
nrow(dummies)
total_Jamaica <- merge(Jamaica, dummies, by=0, all=TRUE)
#total_Jamaica<-merge(Jamaica,dummies)
nrow(total_Jamaica)
total_Jamaica
```
```{r}
reg<-lm(trade~distance+gdp_part+gdpp_part+gatt_defacto+gatt_dejure_part+commodity.24321+commodity.24322+commodity.71931+commodity.71842+commodity.72952, data = total_Jamaica)#commodity.68212+commodity.72952+commodity.73291+commodity.73492+commodity.84111+commodity.84112+commodity.84144+commodity.85102+commodity.89111
summary(reg)
```
###########################################################################









#We obtain total trade figures by commodity type

```{r}
jam = select(Jamaica, year,comm_code, part_code,trade,gatt_dejure_rep)
jam
```

```{r}
jam1<-aggregate(jam$trade,by = (jam[2]),sum)
jam1<-jam1 #%>%#rename(trade = x)
jam1
```
#We ORDER this table by trade amount
```{r}
jam2<-jam1[order(-jam1$x),]
jam2
```
#We obtain total trade figures by partner country

```{r}
jam3<-aggregate(jam$trade,by = (jam[3]),sum)
jam3<-jam3 %>%
  rename(trade = x)
jam3
```
#SORTED TRADING PARTNERS, BY NO SURPRISE USA ON TOP
```{r}
jam4<-jam3[order(-jam3$trade),]
jam4
```
#FULL TRADE BY COMMODITY CODE
```{r}
Trade = select(Jamaica, year,comm_code,trade,part_code)
Trade
```
#this is trade by commodity code
```{r}
Trade_sorted<-Trade[order(Trade$year,Trade$comm_code),]
Trade_sorted
by_commo <-Trade_sorted %>% group_by(comm_code)
```



























#summarise(.jam, ...)
jam1<-aggregate(jam$trade,by = (jam[2:3]),sum)
jam1<-jam1 %>%
  rename(trade = x)
jam1
#gatt_yes=gatt_yes[order(gatt_yes$year),]
#jam1<-group_by(jam[,3:4], by = (jam[1:2]), sum)
#jam1
#jam1<-jam1[order(jam1$trade)]

```
```{r}
jam2<-jam1[order(-jam1$trade),]
jam2
```

```{r}
#jam3<-aggregate(jam1$trade,by = (jam[1]), sum)
jam3<-aggregate((jam1$trade),list(jam1$comm_code),sum)
jam3
```
```{r}
jam5<-aggregate((jam1$trade),list(jam1$part_code),sum)
jam5
plot(jam5)
```
```{r}
partners<-t(jam5)
partners
```
```{r}
barplot(t(jam5))
```

```{r}
jam4<-jam3[order(jam3$Group.1),]
jam4
```

```{r}
t(jam4)
```

```{r}
barplot(t(jam4))
plot(t(jam4))
#lm(x~Group.1)
```
eq<-lm(jam2$trade~partners[1:44])
```{r}
#eq<-lm(jam2$trade~partners[1]+partners[2]+partners[3]+partners[4])
```

